---
title: "Unit_3"
author: "Fabio"
date: "5/24/2019"
output: html_document
---
##Unit_3

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '~')
```

#Question 1 
It is cloned in localdrive(the titanic table)

"Desktop/USM/Unit_3/questio_1/awesome-public-datasets/Datasets/titanic.csv"

#Question2


*A The table was read and inspected

```{r, echo=TRUE}
tdf = read.csv("~/Desktop/USM/Unit_3/questio_1/awesome-public-datasets/Datasets/titanic.csv", header = TRUE, sep = ",")
str(tdf)
colnames(tdf)

```
*B The respective count of females and males aboard the Titanic. 

```{r, echo=TRUE}
plot(tdf$Sex, xlab= "Female", ylab= "Male", main="Sex Distribution in the Titanic" )

```


*C Mean Age,Fare, and Survival for the titanic tripulation



```{r, echo=TRUE}
#Without the apply function
meanAge<-mean(tdf$Age, na.rm=TRUE)
meanAge
meanFare<-mean(tdf$Fare, na.rm=TRUE)
meanFare
# With the apply function
asf <- tdf[c("Age","Survived","Fare")]
asf <- na.omit(asf)
head(asf)
meanVar<-lapply(asf, mean)
meanVar

```


#Question 3
*This is the funtion to get information from the sleep study. We look at "MedianAge","MinDuration","MaxDuration","DurationRange", "SelfEsteem","SE_SD 

```{r, echo=TRUE}
sdf = read.csv("Desktop/USM/Unit_3/sleep_data_01.csv", header=TRUE, sep=",")
head(sdf)
SleepDf  <- function(df,x,y,z){
  median <- median(na.omit(df[,x]))
  min  <- min(na.omit(df[,y]))
  max  <- max(na.omit(df[,y]))
  ranged<-range(na.omit(df[,y]))
  mean <-mean(na.omit(df[,z]))
  std  <-sd(na.omit(df[,z] ))
  report  <- data.frame(median, min, max, ranged, mean, std)
  colnames(report)<-c("MedianAge","MinDuration","MaxDuration","DurationRange", "SelfEsteem","SE_SD")
  return(round(report, digits = 2))
}
SleepDf(sdf,"Age", "Duration", "RSES")

```


#Question 4


*A Install the "fivethirtyeight" package 



*B The data have 21 variables and 173 observations of college student graduatyes.It describe demographic, major, major category, employment, types of employments, wages and rank.



```{r, echo=TRUE}
library(fivethirtyeight)
data(package = "fivethirtyeight")
vignette("fivethirtyeight", package = "fivethirtyeight")
data(college_recent_grads)
head(college_recent_grads)
dfc<-data.frame(college_recent_grads)
head(dfc)

```



```{r, echo=TRUE}
str(college_recent_grads)

```


*C Inspect the dataframe.


```{r, echo=TRUE}
dim(dfc)

```
#Question 5

*A Inspect the data frame about college graduate


```{r, echo=TRUE}
colnames(dfc)
length(colnames(dfc))

```

*B Unique major_category in the data frame about college graduate

```{r, echo=TRUE}
unique(dfc$major_category)
MajorCount<- aggregate(data.frame(count = dfc$major_category), list(value = dfc$major_category), length)
MajorCount
```



*C Plot about the Major Category for colleges graduates



```{r , echo= TRUE}
par(las=2) 
barplot(height = MajorCount$count, width = 1, space = NULL, names.arg = MajorCount$value,
        main = "Major Category for Recent Colleges Graduates", xlab = "Value", legend.text = "Categoty", 
        col = "darkmagenta", axes = TRUE, horiz = TRUE, srt=60, las= 2, cex.names = 0.6)
```



*D Print the "fivethirtyeight" to a csv



```{r, echo=TRUE}
write.csv(dfc, file = "Datafive.csv",row.names=FALSE)

```
#Question 6

https://github.com/savorgnan5/USM.git
