---
title: "LIve Session 2 CLT"
author: "Bivin"
date: "9/6/2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Simulator to Demonstrate CLT

## Control Parameters
```{r}
n = 7 # sample size per sample
simulations = 10000 #number of samples and thus number of xbars we will generate.  
mu = 21; # mean parameter for use with normal distribuions
sigma = 7.08; # standard deviation parameter for use with normal distribuions
```

## Data Holder
```{r}
xbar_holder = numeric(simulations) # This will hold all the sample means.
```

## Simulate and Store
Generate 1000 samples each of size 10 and find the mean of each sample.  Then store each mean in the xbar_holder vector.

```{r}
for (i in 1:simulations)
{ 
  sample = rnorm(n,mean = mu, sd = sigma)
  xbar = mean(sample)
  xbar_holder[i] = xbar
}
```

## display the distribution of sample means (plot a histogram of the sample means)
```{r}
hist(xbar_holder, col = "blue", main = paste("Distribution of the sample mean: n = ", n), xlab = "Sample Means", xlim = c(10,31))
```

## summary statistics of the distribution of the simulated sample means. 
```{r}
summary(xbar_holder)
```

##  The Pvalue!
The probability of observing a result as extreme or more extreme than what was observed assuming the null hypothesis is true. 
```{r}
pvalue = length(which(xbar_holder>29.86))/simulations
pvalue
```

