---
title: "Unit 5 Assignment"
author: "Fabio"
date: "6/7/2019"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Dependencies



```{r echo = TRUE}
library(dplyr)
library(tidyverse)
```



###Data Youb2016


###Data Youb2015

```{r echo=TRUE}
url<-"https://raw.githubusercontent.com/BivinSadler/MSDS-6306-Doing-Data-Science/master/Unit%205/yob2016.txt"
data <- read.csv(url(url), sep = ";", header = F)
head(data)

url1<-"https://raw.githubusercontent.com/BivinSadler/MSDS-6306-Doing-Data-Science/master/Unit%205/yob2015.txt"
data1 <- read.csv(url(url1), sep = ",", header = F)
head(data1)
```

#Question 1



###1A,1B



### Load the data above. Change the column name. Display the summary and the structure of the data


```{r , echo=TRUE}
class(data)
colnames(data)<- c("Name", "Gender", "Number of Children")
head(data)
summary(data)
str(data)
```


###1C,1D



###Find the misspelled name, and erase it.The final data is saved as an object under finalData1


```{r , echo=TRUE}
ms<-grep(".*yyy.*", data$Name)
ms
data<-data[-ms,]
head(data)
finalData<- data
head(finalData)
```


#Question2


###2A,2B The file 2015 is loaded above.It is put in a dataframe.


###2B The last 10 rows are all males, and small number, very unusual name to me.


```{r , echo=TRUE}
class(data1)
colnames(data1)<- c("Name", "Gender"," Number of Children") 
tail(data1, 10)
```


###2C Mege the 2 datas by the name, change the callumn name and erase the Na



```{r , echo=TRUE}
final<- merge(data, data1, by ="Name" )
head(final)
final[, "Gender.x"]<-NULL
names(final)<- c("Name", "Number of Children 2016", "Gender", "Number of Children 2015")
head(final)
head(is.na(final))
final<- na.omit(final)
head(final)
```


#Question 3

###3A


###Get the total number of name per year


```{r , echo=TRUE}
final %>% mutate(Total = `Number of Children 2016` + `Number of Children 2015`) -> FinalFinal
head(FinalFinal)
class(FinalFinal)
```


###3B


###Sort it by top 10 names



```{r , echo=TRUE}
FinalFinal %>% arrange(desc(Total))-> FinalFinal
head(FinalFinal)
```



###3C


###Filter the data only by female, eliminate male.



```{r , echo=TRUE}
FinalFinal %>% filter(Gender == 'F') %>% arrange(desc(Total)) -> FinalFinal
head(FinalFinal)
```


###3D


###Getting the top ten females names, clean it and write in a csv file.


```{r , echo=TRUE}
top_names<- top_n(FinalFinal, 10, Total)
top_names[,"Number of Children 2016" ]<-NULL
top_names[,"Number of Children 2015" ]<-NULL
top_names[,"Gender"]<-NULL
top_names
write.csv(top_names, file = "Top 10 names")
```


# Questio 4

https://github.com/savorgnan5/USM/tree/master/Unit_5

